Analyses

### 2024-07-19 src/analysis/Analysis.Rmd
update analyses

```{r "balance-checks", fig.height=12, fig.width=8}
#source(here("src/analysis/balance-test.R"))
#df
```

@@

>>>>

```{r "balance-checks", fig.height=12, fig.width=8}
source(here("src/analysis/balance-test.R"))
df
```

@@

```{r "explore-profiles", fig.height=7, fig.width=8}
source(here("src/analysis/profiles.R"))
prof1 
prof2
```
